CFF GCT Study

### 2025-07-28 Christine Chan/CFF GCT Study/cff_gct_analysis.qmd
updated GCT figures

```{r}
#| warning: false
# The code below is a total mess because Larry keeps sending requests -
# clean up later
plot_df <- df %>%
  pivot_longer(c(`OGTT 0 min`, `OGTT 60 min`, `OGTT 120 min`),
    names_to = "OGTT Timepoint", values_to = "Glucose"
  )
plot_df$`OGTT Timepoint` <- factor(plot_df$`OGTT Timepoint`,
  levels = c("OGTT 0 min", "OGTT 60 min", "OGTT 120 min"),
  labels = c("Fasting", "OGTT-1hG", "OGTT-2hG")
)
box_p <- ggplot(
  plot_df,
  aes(x = `OGTT Timepoint`, y = Glucose, fill = `OGTT Timepoint`)
) +
  geom_boxplot() +
  ylab("Glucose (mg/dL)") +
  scale_y_continuous(breaks = c(100, 140, 200, 300)) +
  scale_fill_manual(values = RColorBrewer::brewer.pal(3, "Paired")) +
  facet_wrap(~Diabetes) +
  theme_bw(base_size = 20) +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.x = element_blank()
  )
box_p
ggsave("./Christine Chan/CFF GCT Study/Dissemination/Figures/boxplot.png",
  box_p,
  device = "png"
)
# Dotplot
dotplot <- ggplot(df, aes(x = Diagnosis, y = `GCT 60 min plasma`)) +
  geom_point() +
  geom_hline(yintercept = 140, linetype = "dashed") +
  geom_hline(yintercept = 150, linetype = "dashed") +
  geom_hline(yintercept = 160, linetype = "dashed") +
  geom_hline(yintercept = 147, linetype = "dashed", size = 1) +
  ylab("GCTpl (mg/dL)") +
  theme_bw() +
  scale_y_continuous(breaks = c(100, 140, 147, 150, 160))

@@

dotplot +
  theme(text = element_blank())

@@

dot_p1 <- ggplot(

@@

@@

dot_p2 <- ggplot(

@@

    axis.title.x = element_blank(),
    axis.title.y = element_blank()

@@

dot_p3 <- ggplot(

@@

    axis.title.x = element_blank(),
    axis.title.y = element_blank()

@@

dot_p4 <- ggplot(

@@

    axis.title.x = element_blank(),
    axis.title.y = element_blank()

@@

dot_p5 <- ggplot(

@@

@@

dot_p <- dot_p1 + dot_p2 + dot_p3 + dot_p4 + dot_p5 + plot_layout(ncol = 5)

@@

>>>>

```{r}
# The code below is a total mess because Larry keeps sending requests -
# clean up later
  pivot_longer(c(`OGTT 0 min`, `OGTT 60 min`, `OGTT 120 min`),
  levels = c("OGTT 0 min", "OGTT 60 min", "OGTT 120 min"),
  labels = c("Fasting", "OGTT-1hG", "OGTT-2hG")
  scale_fill_manual(values = RColorBrewer::brewer.pal(3, "Paired")) +
dotplot <- ggplot(df, aes(
  x = Diagnosis, y = `GCT 60 min plasma`,
  colour = Diagnosis
)) +
  geom_hline(yintercept = 130, linetype = "dashed") +
  geom_hline(yintercept = 160, linetype = "dashed") +
  geom_hline(yintercept = 147, linetype = "dashed", size = 1) +
  ylab("GCTpl (mg/dL)") +
  theme_bw() +
  scale_y_continuous(breaks = c(100, 130, 147, 160)) +
  scale_color_manual(values = c("#264653", "#2a9d8f", "#e9c46a", "#f4a261", "#e76f51"))

@@

ggsave("./Christine Chan/CFF GCT Study/Dissemination/Figures/dotplot.png",
  dotplot,
  height = 4, width = 6, units = "in", dpi = 600,

@@

dot_rpg <- ggplot(

@@

    plot.title = element_text(hjust = 0.5),
    axis.title.x = element_blank(), axis.text.x = element_blank(),
    axis.ticks.x = element_blank()

@@

dot_gctpl <- ggplot(

@@

    plot.title = element_text(hjust = 0.5),
    axis.title.y = element_blank(), axis.text.y = element_blank(),
    axis.title.x = element_blank(), axis.text.x = element_blank(),
    axis.ticks.x = element_blank()

@@

dot_rcg <- ggplot(

@@

    axis.title.y = element_blank(), axis.text.y = element_blank(),
    axis.title.x = element_blank(), axis.text.x = element_blank(),
    axis.ticks.x = element_blank()

@@

dot_gctcap <- ggplot(

@@

    plot.title = element_text(hjust = 0.5),
    axis.title.y = element_blank(), axis.text.y = element_blank(), 
    axis.ticks.y = element_blank(),
    axis.title.x = element_blank(), axis.text.x = element_blank(),
    axis.ticks.x = element_blank()

@@

dot_hba1c <- ggplot(

@@

    axis.text.x = element_blank(),
    axis.title.x = element_blank(), axis.ticks.x = element_blank()

@@

dot_p <- dot_rpg + dot_rcg + dot_gctpl + dot_gctcap + dot_hba1c + 
  plot_layout(ncol = 5,guides = 'collect')

@@

  dot_p,
  height = 9, width = 12, units = "in", dpi = 600,
